Dark matter halo concentrations with a bayesian approach

### 2014-09-12 paper/article.tex
corrected mistake
new plots

It is also customary to express the mass of the halo inte terms of the
circular velocity $V_{c}=sqrt{GM(<r)/r}$. From this we can
define a new dimensionless circular velocity $v(<x)\equiv
V_{c}(<r)/V_{c}(<r_v)$, using the result in Equation \ref{eq:profile}
to have:

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{density-mass.pdf}
\end{center}
\caption{Concentration obtained from the mass method against the one obtained in the density method
    \label{fig:density-mass}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
\end{center}
\caption{Concentration obtained from the velocity method against the one obtained in the density method
    \label{fig:density-velocity}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{velocity-mass.pdf}
\end{center}
\caption{Concentration obtained from the mass method against the one obtained in the velocity method
    \label{fig:velocity-mass}}
\end{figure}

>>>>

It is also customary to express the mass of the halo inte terms of the
circular velocity $V_{c}=\sqrt{GM(<r)/r}$. From this we can
define a new dimensionless circular velocity $v(<x)\equiv
V_{c}(<r)/V_{c}(<r_v)$, using the result in Equation \ref{eq:profile}
to have:

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{mass-density.pdf}
\end{center}
\caption{Concentration obtained from the density method against the one obtained in the mass method
    \label{fig:density-mass}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
\end{center}
\caption{Concentration obtained from the velocity method against the one obtained in the density method
    \label{fig:density-velocity}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{velocity-mass.pdf}
\end{center}
\caption{Concentration obtained from the mass method against the one obtained in the velocity method
    \label{fig:velocity-mass}}
\end{figure}
